---
title: "HW6"
author: "Sagar Ganapaneni"
date: "November 15, 2016"
output: word_document
---



```{r}
x = -2:2
y = c(1 + 0 + 0, # x = -2
      1 + 0 + 0, # x = -1
      1 + 1 + 0, # x = 0
      1 + (1-0) + 0, # x = 1
      1 + (1-1) + 0 # x =2
      )
y = x*
plot(x,y)
  
```

problem 3:

```{r}
set.seed(12)
library(ISLR)
library(glmnet)
library(boot)
data(Auto)
summary(Auto)
pairs(Auto, main='Scatterplot for Auto Data')

```
Wa may see that "mpg" is negatively correlated to "cylindes", "displacement", "horsepower" and "weight". We begin by performing polynomial regression of "mpg" vs "displacement".


Polynomial function

```{r}

MSE <- rep(NA, 15)
for (i in 1:15) {
    fit <- glm(mpg ~ poly(displacement, i), data = Auto)
    MSE[i] <- cv.glm(Auto, fit, K = 10)$delta[1]
}
plot(1:15, MSE, xlab = "Degree", ylab = "Test MSE", type = "l", main = "Polynomical Degree vs Test MSE")
points(which.min(MSE), MSE[which.min(MSE)], col = "red", cex = 2, pch = 20)
```

The optimal degree for the polynomial here is 10th degree with CV TEST MSE:

```{r}
MSE[which.min(MSE)]
```


Step function

```{r}
MSE <- rep(NA, 15)
for (i in 2:15) {
    Auto$dis_cut <- cut(Auto$displacement, i)
    fit <- glm(mpg ~ dis_cut, data = Auto)
    MSE[i] <- cv.glm(Auto, fit, K = 10)$delta[1]
}
plot(2:15, MSE[-1], xlab = "Cuts", ylab = "Test MSE", type = "l", main = "# Cuts vs Test MSE")
points(which.min(MSE), MSE[which.min(MSE)], col = "red", cex = 2, pch = 20)

```
We may see that the error is minimum for 9 cuts with CV TEST MSE

```{r}
MSE[which.min(MSE)]
```


Spline functions

```{r}
library(splines)
MSE <- rep(NA, 20)
for (i in 3:20) {
    fit <- glm(mpg ~ ns(displacement, df = i), data = Auto)
    MSE[i] <- cv.glm(Auto, fit, K = 10)$delta[1]
}
plot(3:20, MSE[-c(1, 2)], xlab = "degrees of freedom", ylab = "Test MSE", type = "l", main="Test MSE vs Splines degree of freedom")
d.min <- which.min(MSE)
points(which.min(MSE), MSE[which.min(MSE)], col = "red", cex = 2, pch = 20)

```
We may see that the error is minimum for 9 degrees of freedom with CV TEST MSE

```{r}
MSE[which.min(MSE)]
```

Plotting X vs. the non-linear estimate f^(X)
```{r}
    fit <- glm(mpg ~ ns(displacement, df = which.min(MSE)), data = Auto)
    par(mfrow = c(2,2))
    plot(fit)
```

GAM

```{r}
library(gam)
fit <- gam(mpg ~ s(displacement, 4) + s(horsepower, 4), data = Auto)
summary(fit)
```

```{r}
library(DAAG)
lm_fit <- lm(mpg ~ displacement, data = Auto)
a<-cv.lm(data = Auto, form.lm = formula(mpg ~ displacement),m=10)

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
