---
title: "HWp5"
author: "Sagar Ganapaneni"
date: "November 15, 2016"
output: word_document
---
Problem 5:
This question relates to the College data set.

(a)Split the data into a training set and a test set. Using out-of-state
tuition as the response and the other variables as the predictors,
perform forward stepwise selection on the training set in order
to identify a satisfactory model that uses just a subset of the
predictors.

```{r}
library(ISLR)
library(leaps)
library(gam)
data("College")
attach(College)
train <- sample(length(Outstate), length(Outstate) / 2)
test <- -train
College_train <- College[train, ]
College_test <- College[test, ]
fit <- regsubsets(Outstate ~ ., data = College_train, nvmax = 17, method = "forward")
fit.summary <- summary(fit)
par(mfrow = c(1, 3))
plot(fit.summary$cp, xlab = "Number of variables", ylab = "Cp", type = "l")
min_cp <- min(fit.summary$cp)
std_cp <- sd(fit.summary$cp)
abline(h = min_cp + 0.2 * std_cp, col = "red", lty = 2)
abline(h = min_cp - 0.2 * std_cp, col = "red", lty = 2)
plot(fit.summary$bic, xlab = "Number of variables", ylab = "BIC", type='l')
min_bic <- min(fit.summary$bic)
std_bic <- sd(fit.summary$bic)
abline(h = min_bic + 0.2 * std_bic, col = "red", lty = 2)
abline(h = min_bic - 0.2 * std_bic, col = "red", lty = 2)
plot(fit.summary$adjr2, xlab = "Number of variables", ylab = "Adjusted R2", type = "l", ylim = c(0.4, 0.84))
max_adjR2 <- max(fit.summary$adjr2)
std_adjR2 <- sd(fit.summary$adjr2)
abline(h = max_adjR2 + 0.2 * std_adjR2, col = "red", lty = 2)
abline(h = max_adjR2 - 0.2 * std_adjR2, col = "red", lty = 2)
```
Cp, BIC and adjr2 show that size 6 is the minimum size for the subset for which the scores are within 0.2 standard deviations of optimum.


```{r}
fit <- regsubsets(Outstate ~ ., data = College, method = "forward")
coeffs <- coef(fit, id = 6)
names(coeffs)
```

(b) Fit a GAM on the training data, using out-of-state tuition as the response and the features selected in the previous step as the predictors. Plot the results, and explain your findings.

```{r}
fit <- gam(Outstate ~ Private + s(Room.Board, df = 2) + s(PhD, df = 2) + s(perc.alumni, df = 2) + s(Expend, df = 5) + s(Grad.Rate, df = 2), data=College_train)
par(mfrow = c(2, 3))
plot(fit, se = T, col = "blue")
```
(c) Evaluate the model obtained on the test set, and explain the results obtained.

```{r}
preds <- predict(fit, College_test)
err <- mean((College_test$Outstate - preds)^2)
err
```

```{r}
tss <- mean((College_test$Outstate - mean(College_test$Outstate))^2)
rss <- 1 - err / tss
rss
```
We obtain a test R^2 of 0.77 using GAM with 6 predictors.


```{r}
summary(fit)
```
ANOVA shows a strong evidence of non-linear relationship between "Outstate" and "Expend"", and a moderately strong non-linear relationship (using p-value of 0.05) between"Outstate" and "Grad.Rate"" or "PhD".

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
